Serpe SC data

### 2025-02-10 SerpeSCdata.Rmd
update

gene.name = "burs"

@@

heat.data = na.omit(serpe[heat.genes,])

@@

Cluster.id = c(serpe.annotated.names)

Cluster.labelcolor = c(rep("darkgreen", length(serpe.annotated.names)))

@@

@@

heatmap.2(heat.data,
        Colv = NA,
        #Rowv = NA,
        labCol = Cluster.id,
        scale = 'none',
        ColSideColors = Cluster.labelcolor,
        trace = "none",
        col = heat.colors(numcols),
        dendrogram = "none",
        na.color = "white",
        key.title = "Mean Expression",
        colCol = Cluster.labelcolor,
        margins = c(10, 5), 
        #colsep = c(18, 46, 95),
        #sepcolor = "black",
        breaks = color.breaks)
legend("left",
       title = "Cell Types",
       legend = c("Manually Currated"),
       fill = c("darkgreen"),
       xpd = T)
#library(corrplot)
#corrplot(heat.data, is.corr = F, col =COL2("RdBu", 200))

>>>>

gene.name = "Burs"

@@

```{r echo = F, fig.width=10, fig.height=16}

heat.genes = c("VGlut", "ChAT", "VAChT", "VGAT", "Gad1", "DAT", "ple", "SerT", "Hdc", "dimm", "Burs")

heat.data = na.omit(serpe.inter[heat.genes,])

heat.data = apply(heat.data, MARGIN = 2, as.numeric)
#heat.data = log10(heat.data)
row.names(heat.data) = heat.genes

@@

Cluster.id = colnames(serpe.inter)

Cluster.labelcolor = c(rep("darkgreen", ncol(serpe.inter)))

heat.colors = colorRampPalette(c("grey95", "steelblue", "gold", "red3"))
heat.colors = colorRampPalette(c("white", "darkgreen", "darkgreen"))

@@

max.break = log10(max(log10(heat.data)))

@@

color.breaks = 10^(c(0:(numcols))*(max.break/(numcols + 1)))

heat.data = t(heat.data)

numcols = 75

heatmap.2(log10(heat.data),
        Colv = NA,
        Rowv = NA,
        #labCol = Cluster.id,
        scale = "none",
        #ColSideColors = Cluster.labelcolor,
        trace = "none",
        col = heat.colors(numcols),
        dendrogram = "none",
        na.color = "white",
        key.title = "Mean Expression")#,
        #colCol = Cluster.labelcolor,
        #margins = c(10, 5), 
        #colsep = c(18, 46, 95),
        #sepcolor = "black",
        #breaks = color.breaks)
        #breaks = c(0:numcols))
legend("left",
       title = "Cell Types",
       legend = c("Interneurons"),
       fill = c("darkgreen"),
       xpd = T)
#library(corrplot)
#corrplot(heat.data, is.corr = F, col =COL2("RdBu", 200))
